---
title: "p8105_hw1_xq2241"
author: "Xinghao Qiao"
date: 2024-09-13
output: github_document
---


# Question 1 

```{r}
#import data
data("penguins", package = "palmerpenguins")

# Variables in the dataset
variables <- names(penguins)

# Size of the dataset
num_rows <- nrow(penguins)
num_cols <- ncol(penguins)

# Mean flipper length
mean_flipper_length <- mean(penguins$flipper_length_mm,na.rm=T)



```

*   Description of the data set

    * Variables:we have 8 types of variables in the penguins dataset, which are 'species','island',bill_length_mm','bill_depth_mm','flipper_length_mm','body_mass_g','sex' and 'year'.

    * Size of dataset: 8 columns and 344 rows
    * Mean flipper length: 200.9152 mm
*  Scatterplot of flipper_length_mm (y) vs bill_length_mm (x) 
```{r}
library(ggplot2)
penguin_p <- ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +geom_point()+
  labs(title = "Flipper Length vs Bill Length", x = "Bill Length (mm)", y = "Flipper Length (mm)") 

print(penguin_p)

# Save the plot
ggsave("penguin_scatterplot.png", plot = penguin_p)

```
# Question 2

First, we create a data frame,
```{r}
library(tidyverse)

# Create a random sample of size 10 from a standard Normal distribution
set.seed(300)  
random_s <- rnorm(10)

# Create a logical vector indicating whether elements of the sample are greater than 0
logical_vector <- random_s > 0

# Create a character vector of length 10
character_vector <- letters[1:10]

# Create a factor vector of length 10 with 3 different levels
factor_vector <- factor(rep(c("A", "B", "C"), length.out = 10))

# Combine the data
frame <- data.frame(random_s, logical_vector, character_vector, factor_vector)
frame


```
Then, we try to calculate the mean of each varialbe,
```{r}
mean(frame$random_s)       # This works, since it's numeric
mean(frame$logical_vector)      # This works, as TRUE is 1 and FALSE is 0
mean(frame$character_vector)    # This doesn't work, since the varialbe are characters
mean(frame$factor_vector)       # This doesn't work, as factors are 3 categorical

```
In this case, only random samples and logicla vector can be caculated, because the rest two varialbes are not numeric.
Now we try to use 'as.numeric' function to the logical, character, and factor variables. Logical vector and factor vector can be caculated, but character vector can not be calculated.
```{r eval = FALSE}

# Apply as.numeric 
numeric_logical <- as.numeric(frame$logical_vector)
numeric_character <- as.numeric(frame$character_vector)  
numeric_factor <- as.numeric(frame$factor_vector)

mean(numeric_logical)
mean(numeric_character) 
mean(numeric_factor)


```
In summary, only the numeric varialbes can be caculated.







